Online appendix for "Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2023-05-05 manuscript/appendix.qmd
Add actual OSF DOI

Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion statistical analysis compendium at <https://doi.org/10.17605/OSF.IO/MTR6X>. Our general modeling approach can be summarized as follows:

>>>>

Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion statistical analysis compendium at <https://doi.org/10.17605/OSF.IO/AQVNK>. Our general modeling approach can be summarized as follows:
